\documentclass[options]{article}
\usepackage[parfill]{parskip}
\pagenumbering{roman}
\title{Firebase For Application Development! How effective are its services?}
\author{Azamuke Denish\thanks{supervisor: Ernest Mwebaze}}\newpage
\date{%
    Makerere University\\%
    Mar 8, 2018
}
\begin{document}
\begin{titlepage}
\maketitle
\end{titlepage}
\newpage

\section{Introduction}
Firebase evolved from Envolve, a prior startup founded by James Tamplin and Andrew Lee in 2011\cite{kanwal2017app}. Envolve provided developers an API that enables the integration of online chat functionality into their websites. \cite{kumar2016implementing}Firebase is a mobile and web application development platform acquired by Google in 2014\cite{anupamasmart}. Some of its services include the following:
\begin{itemize}
    \item Deploy your endpoint rapidly and seamlessly, with minimal time spent configuring CLI settings or importing additional libraries
    \item Effortlessly integrate with other Firebase cloud services such as Firebase Real Time Database
    \item Computing resources are automatically scaled according to your app's usage, so you don't need to worry about server maintenance at all
    \item Setup fulfillment without providing a credit card or billing information
    \item Firebase Cloud Messaging\cite{moroney2017firebase}
    \item \cite{rojas2016cloud}Firebase Test lab for android- Given the large variety of android devices on the market, Firebase provides a straight forward way of testing product performance on a range of devices

\end{itemize}
\section{Service Satisfaction}
Firebase is known to be the only company in that space\cite{greiff2000name}. All of its features work as  documented.
Published developer reviews show a significant  satisfaction with the product. Paul Bresin from Vocabify(vocabifyapp.com) specifically lauds \cite{hess2016algorithm}Firebase’s beautiful authentication, affordable database solutions, user friendly interface, and easy to use integration libraries.
It offers several of it’s services free of charge. For the case of its paid services, feedback collected from experienced Firebase users\cite{villanes2017software} on stack overflow(www.stackoverflow.com) and Quora (www.quora.com) generally lauded the pay as it allows one to pay for only the resources they use in a given time.\cite{rahmifindoctor}
\section{Conclusion}
As a regular user, I precisely found its services  easy to use and reliable as stated in its documentation\cite{bettinson2017developing}. I therefore recommend its services for application development to many Developers.


\newpage
\bibliographystyle{IEEEtran}
\bibliography{references}

\end{document}
